---
title: "BKM Assignment"
author: "Mustafa Omer Guclu"
date: "8 Nov 2019"
output:
  html_document: default
  pdf_document: default
---

```{r}
#REQUIRED LIBRARIES

library(tidyverse)
library(dplyr)
library(ggplot2 )
library(rvest)
library(stringr)
```
```{r}
##IMPORT AND ORGANIZE DATA

#TO GET LIST OF URL OF BKM  


x <- list()
for (i in 0:9){
  for (k in 1:12) {
x[[paste0("url201",i,"0",k)]]<-paste0("https://bkm.com.tr/secilen-aya-ait-sektorel-gelisim/?filter_year=201",i,"&filter_month=",k,"&List=Listele")
  }
}


```
  Please examine code above with the URL of the BKM Web Page linked below

[BKM Link](https://bkm.com.tr/secilen-aya-ait-sektorel-gelisim/?filter_year=2019&filter_month=6&List=Listele)



```{r}
#GETTING DATA FROM URL LIST AND BINDING TO ALL INVOLVED ONE DATAFRAME
DF<-data.frame(matrix(ncol = 5, nrow = 0))

for (i in x){
 HTML_1<-read_html(i) 
 temp_DF<-html_table(html_nodes(HTML_1, "table"),fill = TRUE)[[4]]
 
 for (n in 1:nrow(temp_DF)){
   temp_DF$date[[n]]<-str_remove_all(gsub(".*year=(.+)&filter_month=", "\\1", i),"[A-Z]|[a-z]|&|=")
 }
 DF<-bind_rows(DF,temp_DF)
}




```
```{r}
#DATA WRANGLING & CONTROL OF FINAL FORM OF DATA

DF$year = substr(DF$date, 1,4)
DF$month = substr(DF$date,start=5,stop=6)
colnames(DF)<-c("Sector","Numb_CC","Numb_DC","Amount_CC","Amount_DC","date","year","month")
DF<-DF%>%filter(Sector!="İşyeri Grubu")%>%filter(Sector!="TOPLAM")%>%filter(Sector!="Lütfen listeyi görebilmek için yukarıdan tarih seçiniz.")
str(DF)
DF$Numb_CC<-gsub("[.]", "",DF$Numb_CC)
DF$Numb_DC<-gsub("[.]", "",DF$Numb_DC)
DF$Amount_CC<-gsub("[.]", "",DF$Amount_CC)
DF$Amount_DC<-gsub("[.]", "",DF$Amount_DC)
DF$Amount_CC<-gsub("[,]", ".",DF$Amount_CC)
DF$Amount_DC<-gsub("[,]", ".",DF$Amount_DC)

DF$Numb_CC<- as.numeric(as.character(DF$Numb_CC))
DF$Numb_DC<- as.numeric(as.character(DF$Numb_DC))
DF$Amount_CC<- as.numeric(as.character(DF$Amount_CC))
DF$Amount_DC<- as.numeric(as.character(DF$Amount_DC))

str(DF)
```

```{r}
##ANALYSIS AND GRAPHS
# Analysis 1 - Yearly Development of Debit and Credit Card Usage

pl_df_sum<-DF%>%group_by(year)%>% summarise(Num_Mio=sum(Numb_CC+Numb_DC),Amount=sum(Amount_CC+Amount_DC))
pl_df_sum$Num_Mio<-round(pl_df_sum$Num_Mio/1000000,3)

#Card Usage / Debit and Credit Card Usage
print.data.frame(pl_df_sum)

ggplot(pl_df_sum) + geom_jitter(aes(x=year,y=Num_Mio,color=year,size=Amount)) +labs(title = "Cards Usage", subtitle = "Debit and Credit Card Usage", caption="(based on data from BKM)", y="Tot. Credit+Debit Card Use (in Mio)", x="Year") 




```


As you can see in the data frame and graph  "Card Usage / Debit and Credit Card Usage" Total usage of debit and credit card is increasing in both way (amount in Mio TL can be seen in size) and (number in Mio in y position) from 2010 to 2019.


```{r}


## Analysis 2 - Yearly Development of Top5 Sector of Debit and Credit Card Usage

filter1<-DF%>% group_by(Sector) %>% summarise(Total_Numb_CC=sum(Numb_CC),Total_Numb_DC=sum(Numb_DC),Total_Amount_CC=sum(Amount_CC),Total_Amount_DC=sum(Amount_DC))%>% arrange(desc(Total_Numb_CC+Total_Numb_DC)) %>% slice(1:5) 

yearly_develpment_fortop5<-DF %>% filter(DF$Sector==filter1$Sector)
yearly_develpment_fortop5$Numb_CC<-round(yearly_develpment_fortop5$Numb_CC/1000000)
yearly_develpment_fortop5$Numb_DC<-round(yearly_develpment_fortop5$Numb_DC/1000000)

ggplot(yearly_develpment_fortop5) + geom_jitter(aes(x=year,y=Numb_CC+Numb_DC,color=Sector,size=Amount_CC+Amount_DC)) +labs(title = "Cards Usage", subtitle = "Top 5 Sector (Debit and Credit Card Usage)", caption="(based on data from BKM)", y="Tot. Credit+Debit Card Use (in Mio)", x="Year") +scale_y_continuous()


```


As you can see in the graph "Card Usage / Top 5 Sector (Debit and Credit Card Usage)" Total usage of debit and credit card is increasing in both way (amount in Mio TL can be seen in size) and (number in Mio in y position) from 2010 to 2019 for Top5 sector. But we look closely to the details: Market/ Retail Shopping is the dominant leader from in those years. Despite the total food shopping transactions sum (Debit + Credit) is second in the list but only in terms of number of transaction not the amount in TL as you can see from graph above.