---
title: "Week6"
output: html_document
---
REQUIRED PACKAGE
```{r}
library(tidyverse) ## dplyr provides the join functions

```




[Data Avaliable Here](https://github.com/pjournal/mef03-MustafaOmerGuclu/blob/master/atp_tennis_data_2017.RData)

After Download Data from Link Above 


Load the data to your Working Directory with code below

```{r}
load("/home/mustafa-omer/İndirilenler/atp_tennis_data_2017.RData") # Change Path according to your data location you may use file.chose() function to reach your data path 
```
DATA EXAMINATION
```{r}
str(player_df)
```

```{r}
str(rank_df)
```
```{r}
str(score_df)
```

```{r}
str(stats_df)
```

```{r}
str(tourney_df)
```
QUESTION-1:
Rank countries (flag cıdes) by the number of singles champions

Solution-1:
```{r}
champ_flags_df<-tourney_df%>%left_join(.,player_df,by=c("singles_winner_player_id"="player_id"))%>%count(flag_code,sort = TRUE)
champ_flags_df
```

QUESTION-2:
Rank countries which did not get any singles championships by the games won when they win the match

Solution-2:
```{r}
nonchamp_players<-player_df%>%select(player_id,flag_code)%>%anti_join(.,champ_flags_df)
loser_countries_rank<-nonchamp_players%>%left_join(.,score_df,by=c("player_id"="winner_player_id"))%>%group_by(flag_code)%>%summarise(total_won=sum(winner_games_won,na.rm = TRUE))%>%arrange(desc(total_won))
loser_countries_rank
```

ANALYSIS-1:
Youngest Winner her/his birth date and name of tournament that s/he won 
```{r}
winner_tourney_match_df<-left_join(tourney_df,player_df,by=c("singles_winner_player_id"="player_id"))
sorted_by_desc_birth_date_winner_df<-winner_tourney_match_df%>%select(first_name,last_name,birth_date,tourney_name)%>%arrange(desc(birth_date))
youngest_winner_birth_date_tourney<-sorted_by_desc_birth_date_winner_df[1,]
youngest_winner_birth_date_tourney
```
ANALYSIS-2:
Best Player of 2017 and Number of succeeded tournaments by her/him
```{r}
success_df<-score_df%>%select(tourney_id,tourney_round_name,winner_player_id)%>%filter(tourney_round_name=="Finals")%>%count(winner_player_id,sort = TRUE)
best_player_2007<-player_df%>%left_join(.,success_df,by=c("player_id"="winner_player_id"))%>%select(first_name,last_name,n)%>%arrange(desc(n))%>%slice(1)
best_player_2007
```

